A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-11 skeleton_and_pathtracing.tex
J'ai avancé dans l'intro

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                        %
%                   INTRODUCTION                         %
%                                                        %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec::intro}
Path tracing algorithms are able to render photorealistic images from a scene description by simulating light propagation. The photorealistic aspect is achieved by simulating diffusion of light: elements of the scene which are illuminated by a light source can cast this light to other elements which are not directly lighted by any light source, thus giving a natural effect of light diffusion. To do so, a path tracing algorithm sends rays (of light) in the scene

The algorithm sends rays of light simulates global illumination effect: parts of the scene which are not directly illuminated by a light source the idea behind the algorithm is very elegant: for each pixel of the image, it throw rays through the pixel and let it bounce over in the scene (like a real ray of light would do). At each bouncethat will bounce on the scene to accumulate lighting exchanges. In order to get fast convergence the rays must be efficiently distributed through the scene, toward the lights. Our idea is to use a curvilinear skeleton of the void of the scene to guide the rays in the correct direction. We start by defining some useful concepts related to path tracing and we present our skeleton based path tracing algorithm.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                        %
%                   INTRODUCTION                         %
%                                                        %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec::intro}
Path tracing algorithms are able to render photorealistic images from a scene description by simulating light propagation. The photorealistic aspect is achieved by simulating diffusion of light: elements of the scene which are illuminated by a light source can cast part of the light they receive. Thanks to this indirect lighting, parts of the scene which are not directly illuminated by any light source actually receive light, thus giving a nice effect of light diffusion and soft shadows to the image.

To do so, a path tracing algorithm sends rays (of light) with a given energy from the camera, and make them bounce around the scene until they encounter a light source. When a ray hit a point of an object, it loses some energy and gathers some information on the object's material. Then, the ray is reemitted in a direction randomly chosen among various possibilities. Once a ray reaches a light source, the information it gathered through its journey in the scene is averaged in order to decide of the colour of the first impact point. This color is then allocated to one of the pixel of the image, and the process is repeated for each pixel of the output image. In order to obtain a realistic result, it is necessary to integrate various bouncing directions for the rays: this is done by sending many rays for a same pixel: the more rays, the longer the algorithm will take to produce an image, but the more realistic (close to the results obtained by reemitting rays in all possible directions) the result will be. A path tracing can be seen as a random walk process.

The bouncing direction of a ray depends on the texture of the hit point: to each texture is associated a probability distribution function which gives, for a given incoming direction, the probability of reemitting the ray in another directions. The bouncing direction is randomly chosen among the possible values of the probability distribution function. Choosing only one bouncing direction produces a sampling effect which creates noise in the resulting image (due to points where unusual directions were chosen): this noise is naturally reduced by shooting more rays per each image pixel, but unless one shoots a big amount of rays per pixels (and waits a long time before obtaining an image), the noise will always be present in the output image.

In order to avoid infinite bouncing of rays in the scene, a lower limit is set for each ray's energy: below this threshold, a ray will be considered to bring a too small contribution to the pixel's color and will be eliminated from the scene. However, a lost ray is as a waste of computation time, and if one wants to speed up the path tracing algorithm, he should try to minimize the amount of lost rays.

%Precomputation time must remain fast > skeleton !!
